---
title: "An Example knitr LaTeX Article"
author: "Christopher Gandrud"
date: "15 January 2015"
output:
  pdf_document:
    latex_engine: xelatex
    number_sections: yes
    toc: yes
  html_document:
    toc: no
linestretch: 2
fontsize: 11pt
bibliography:
- Main.bib
- Packages.bib
---

```{r Global, include=FALSE}
#### Load and cite R packages ####
# Create list of packages
PackagesUsed <- c("knitr", "ggplot2", "repmis")

# Load PackagesUsed and create .bib BibTeX file.
# Note must have repmis package installed.
repmis::LoadandCite(PackagesUsed, file = "Packages.bib", 
                    install = FALSE)

#### Gather Democracy data from Pemstein et al. (2010)
#### # For simplicity, store the URL in an object called 'url'.
url <- "http://bit.ly/1jXJgDh"

# Create a temporary file called 'temp' to put the zip file into.
temp <- tempfile()

# Create a temporary file called 'temp' to put the zip file into.
temp <- tempfile()

# Download the compressed file into the temporary file.
download.file(url, temp)

# Decompress the file and convert it into a data frame
# class object called 'data'.
UDSData <- read.csv(gzfile(temp, "uds_summary.csv"))

# Delete the temporary file.
unlink(temp)
```

> Here is an example of a knittable article class LaTeX document.

# The Graph

I gathered data from @Pemstein2010 on countries' democracy level. They call 
their democracy measure the Unified Democracy Score (UDS). Figure 1 shows the 
mean UDS scores over time for all of the countries in their sample.

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Mean UDS Scores'}
# Graph UDS scores
ggplot(UDSData, aes(x = year, y = mean)) +
        geom_point(alpha = I(0.1)) +
        stat_smooth(size = 2) +
        ylab("Democracy Score") + xlab("") +
        theme_bw()
```

# Appendix: Reproducing the Document

This document was created using the R version 
`r paste0(version$major, ".", version$minor)` and the R package *knitr* 
[@R-knitr]. It also relied on the R packages *ggplot2* [@R-ggplot2] and 
*repmis* [@R-repmis]. The document can be completely reproduced from source 
files available on GitHub at: 
<https://github.com/christophergandrud/Rep-Res-Examples>.
